Hybrid MILP to efficiently and accuratly \\ solve hard DNN verification instances

### 2024-09-19 ICLR25/experiments.tex
update
update a table

We implemented \toolname in Python 3.8, and Gurobi 9.52 was used for solving LP and MILP problems. We conducted our evaluation on an AMD 5975WX  ($32$ cores$@3.6$GHz, 7nm, year 2022) 
with 256 GB of main memory and an NVIDIA RTX 3090 (not used for CMP).

@@

\begin{table}[t!]	
	\centering
	\begin{tabular}{|c||c|c|c|}
		\hline
		\text{Number $K$}  &  \text{Compensate} &  \text{Incoming Weights} \cite{9211410} & \text{Random} \\ \hline
		\hline
		0  &  1.761 & 1.761 & 1.761  \\ \hline
		10  &  1.641 & 1.651 & 1.696  \\ \hline
		20  &  1.517 & 1.557 & 1.619  \\ \hline
		30  &  1.392 & 1.489 & 1.546  \\ \hline
		40  &  1.275 & 1.447 & 1.469  \\ \hline
		50  &  1.158 & 1.426 & 1.388  \\ \hline
		116 (max) &  0.895 & 1.424 (max=$61$) & 0.895  \\ \hline
	\end{tabular}
	\caption{Average uncertainty of $\MILP_Z$ for nodes of the third layer, for $Z$ with $K$ ReLU nodes of the 1st and 2nd layer (compensating strength vs \cite{9211410} vs random choice).}
	\label{tab:example1}
	\vspace{-0.6cm}
\end{table}

@@

We report in Table \ref{tab:example1} the average uncertainty of $\MILP_Z$ following the choice of the $K$ heaviest compensating ReLU nodes in $Z$, vs choosing $K$ nodes from layers $1$ and $2$. We test using compensation, compared with a random choice, and also choice based on strength in \cite{9211410}, defined as $strength(c) = (UB(n)-LB(n))\cdot W_{cd}$. It is however limited to choosing ReLU in the previous layer 2. This choice is fine for few nodes (10,20), as there is a high correlation between $comp(c)$ being high and $W_{cd}$ being high. However, as soon as many nodes can be chosen in $Z$, compensate becomes much more accurate. Even random becomes more accurate as the number of nodes grows, as \cite{9211410} only has access to nodes $c$ in layer 2, and not to nodes $b$ in layer 1.
For comparison, compensate is the most accurate, from 30 nodes, experimentally validating that compensating strength is the important factor to consider.

@@

{\color{red} We report in Table \ref{tab:example1} the average uncertainty of $\MILP_Z$ following the choice of the $K$ heaviest compensating ReLU nodes in $Z$, vs choosing $K$ nodes randomly from layers $1$ and $2$. 
	Moreover, we also compare choosing nodes in the second layer only (using method in paper \cite{9211410}) with choosing nodes in both the first and second layer.

		The method in paper \cite{9211410} use a formula to value different nodes in a layer, and then choose nodes by their values. We can use the same formula in this comparison experiments. Because we only have $\ReLU$ function, that formula can be simplified to: $$V(n) = (UB(n)-LB(n))\cdot W_{nm}.$$ In this formula, $m$ is the target node, and $n$ is one of source nodes in one layer before. We sort all nodes $n$ by their $V(n)$ values, and choose the nodes with larger values.

>>>>

%
We implemented \toolname in Python 3.8, and Gurobi 9.52 was used for solving LP and MILP problems. We conducted our evaluation on an AMD 5975WX  ($32$ cores$@3.6$GHz, 7nm, year 2022) 
with 256 GB of main memory and an NVIDIA RTX 3090 (not used for CMP).

@@

\begin{table}[t!]	
	\centering
	\begin{tabular}{|c||c|c|c|c|}
		\hline
		\text{Number $K$}  &  \text{Without ratio} &\text{With ratio} &  \text{Incoming Weights} \cite{ DivideAndSlide} & \text{Random} \\ \hline
		\hline
		0  &   1.761  & 1.761 & 1.761 & 1.761  \\ \hline
		5  & 1.532  & 1.533 & &   \\ \hline
		10  & 1.371 & 1.373 & 1.651 & 1.696  \\ \hline
		15  & 1.247 & 1.244 &   &   \\ \hline
		20  & 1.145 & 1.136 & 1.557 & 1.619  \\ \hline
		25  & 1.061 & 1.057 &  &   \\ \hline
		30  & 0.989 & 1.067 & 1.489 & 1.546  \\ \hline
		35  & 0.934 & 1.091 &  &   \\ \hline
		40  &  & & 1.447 & 1.469  \\ \hline
		50  &  & & 1.426 & 1.388  \\ \hline
		116 (max) &  0.895 & 0.895 & 1.424 (max=$61$) & 0.895  \\ \hline
	\end{tabular}
	\caption{Average uncertainty of $\MILP_Z$ for nodes of the third layer, for $Z$ with $K$ ReLU nodes of the 1st and 2nd layer (compensating strength vs \cite{ DivideAndSlide} vs random choice).}
	\label{tab:example1}
	\vspace{-0.6cm}
\end{table}

@@

We report in Table \ref{tab:example1} the average uncertainty of $\MILP_Z$ following the choice of the $K$ heaviest compensating ReLU nodes in $Z$, vs choosing $K$ nodes from layers $1$ and $2$. We test using compensation, compared with a random choice, and also choice based on strength in \cite{ DivideAndSlide}, defined as $strength(c) = (UB(n)-LB(n))\cdot W_{cd}$. It is however limited to choosing ReLU in the previous layer 2. This choice is fine for few nodes (10,20), as there is a high correlation between $comp(c)$ being high and $W_{cd}$ being high. However, as soon as many nodes can be chosen in $Z$, compensate becomes much more accurate. Even random becomes more accurate as the number of nodes grows, as \cite{ DivideAndSlide} only has access to nodes $c$ in layer 2, and not to nodes $b$ in layer 1.
For comparison, compensate is the most accurate, from 30 nodes, experimentally validating that compensating strength is the important factor to consider.

@@

{\color{red} We report in Table \ref{tab:example1} the average uncertainty of $\MILP_Z$ following the choice of the $K$ heaviest compensating ReLU nodes in $Z$, vs choosing $K$ nodes randomly from layers $1$ and $2$. 
	Moreover, we also compare choosing nodes in the second layer only (using method in paper \cite{ DivideAndSlide}) with choosing nodes in both the first and second layer.

		The method in paper \cite{ DivideAndSlide} use a formula to value different nodes in a layer, and then choose nodes by their values. We can use the same formula in this comparison experiments. Because we only have $\ReLU$ function, that formula can be simplified to: $$V(n) = (UB(n)-LB(n))\cdot W_{nm}.$$ In this formula, $m$ is the target node, and $n$ is one of source nodes in one layer before. We sort all nodes $n$ by their $V(n)$ values, and choose the nodes with larger values.

### 2024-09-19 ICLR25/introduction.tex

Limitation: We consider DNNs employing the standard ReLU activation function, though our findings should extend to other activation functions, following similar extention by \cite{??}.

>>>>

Limitation: We consider DNNs employing the standard ReLU activation function, though our findings should extend to other activation functions, following similar extention by \cite{DivideAndSlide}.
